A Decentralized Pub/Sub System for Trusted Machine Economy

### 2020-05-13 paper.tex
Fix typos

\section{Introduction}
%TODO: cite examples
In Internet of Things (IoT), the development of machine-to-machine (M2M) technology\cite{M2M}, cyber physical system (CPS)\cite{CPS} and Industry 4.0 grow rapidly. As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets. With the diverse data streams generated by different entities and carried accross organizations among expanding amount of interconnected devices, it is a challenge for data holders to share and track their data assets. Therefore, data marketplace is viewed as a solution to build a secure, reliable and scalable data sharing platform where data providers and data consumers meet.

Among the challenges of data marketplace\cite{BigDataMarket}, we conclude the following four essential requirements of a data marketplace system:
\begin{itemize}
	\item \textbf{Scalability}. 
1) The performance of data marketplace should scale with the massive amount of participants. 2) Keys and entry points of data products managed by participants should be as small as possible. 
	\item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.	
	\item \textbf{Confidentiality}. 
1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.	
	\item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leaked within the subscription history.
	\item \textbf{Economics Incentive}. The economics incentives can encourage the data providers to participate the system and pay more attention on the quilaty control. 
\end{itemize}

In contrast to centralized architectures in \cite{DIaas, IOTAIdustryMarketplace, MARSA} that target to handle static data sets, we proposed a decentralized data marketplace in \cite{MyDataMarketplace} which focuses on processing the high volume, high velocity and high variety of "Big Data" streams\cite{BigData} while fulfills the aforementioned requirements. Moreover, a decentralized architecture can better adapts the dynamic roles than centralized one. See Fig.~\ref{fig:system_design}.

In the previous paper, we investigated the use of decentralized publish/subscribe (pub/sub) model and distributed ledger techonologies (DLTs) to construct the authority-less and trusted infrastructure, particularly Ethereum Smart Contract\cite{smartContract} and IOTA Masked Authenticated Messaging (MAM)\cite{MAM}. The pub/sub model features the scalability and resource-effieciency, and the economic incentives are stimulated by regulating trading agreement and penalty on Ethereum Smart Contracts with transparency. Lastly, MAM as the data storage not only ensures the data integrity, enables access control and provides a scalable key and data management. These three keys meet the requirements metioned previously.

>>>>

\section{Introduction}
%TODO: cite examples
In the Internet of Things (IoT), the development of machine-to-machine (M2M) technology\cite{M2M}, cyber physical system (CPS)\cite{CPS} ,and Industry 4.0 grow rapidly. As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories ,and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets. With the diverse data streams generated by different entities and carried across organizations among expanding the amount of interconnected devices, it is a challenge for data holders to share and track their data assets. Therefore, data marketplace is viewed as a solution to build a secure, reliable and scalable data sharing platform where data providers ,and data consumers meet.

Among the challenges of data marketplace\cite{BigDataMarket}, we conclude the following four essential requirements of a data marketplace system:
\begin{itemize}
	\item \textbf{Scalability}. 
1) The performance of data marketplace should scale with the massive amount of participants. 2) The keys and entry points of data products managed by participants should be as small as possible. 
	\item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.	
	\item \textbf{Confidentiality}. 
1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.	
	\item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leak within the subscription history.
	\item \textbf{Economics Incentive}. The economic incentives can encourage the data providers to participate in the system and pay more attention to the quality control. 
\end{itemize}

In contrast to centralized architectures in \cite{DIaas, IOTAIdustryMarketplace, MARSA} that target to handle static data sets, we proposed a decentralized data marketplace in \cite{MyDataMarketplace} which focuses on processing the high volume, high velocity and high variety of "Big Data" streams\cite{BigData} while fulfills the aforementioned requirements. Moreover, a decentralized architecture can better adapt the dynamic roles than a centralized one. See Fig.~\ref{fig:system_design}.

In the previous paper, we investigated the use of decentralized publish/subscribe (pub/sub) model and distributed ledger technologies (DLTs) to construct the authority-less and trusted infrastructure, particularly Ethereum Smart Contract\cite{smartContract} and IOTA Masked Authenticated Messaging (MAM)\cite{MAM}. The pub/sub model features the scalability and resource-efficiency, and the economic incentives are stimulated by regulating trading agreement and penalty on Ethereum Smart Contracts with transparency. Lastly, MAM as the data storage not only ensures the data integrity, but also enables access control and provides a scalable key and data management. These three keys meet the requirements mentioned previously.
